%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Aman Meenia} \\ \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 7006718112 ~ 
    \href{mailto:amanmeenia09876@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{amanmeenia09876@gmail.com}} ~ 
    \href{https://linkedin.com/in/aman-meenia-b32a00206/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/aman-meenia}} \\  \vspace{3pt}
    \href{https://github.com/Aman-Meenia}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Aman-Meenia}} ~
    \href{https://amanmeenia.com}{\raisebox{-0.2\height}\faGlobe\ \underline{amanmeenia.com}}
    \vspace{-8pt}
\end{center}



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Government College of Engineering and Technology Jammu}{Sep. 2020 -- July 2024}
      {Bachelor of Technology in Computer Science (CGPA: 8.5 / 10)}{Jammu, Jammu and Kashmir}
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VJV IT Solutions}{Jan. 2025 -- Present}
      {Software Engineer}{Remote}
      \resumeItemListStart
        \resumeItem{Led frontend development for \textbf{Jiva Sync}, an AI-powered matchmaking platform for event-based connections. Architected user flows and responsive SPA components using \textbf{ReactJS}, implementing modern UI/UX for profile onboarding, matchmaking, and event registrations.}
        \resumeItem{Designed the system flow for event registration, including capacity checks, idempotent registration handling, and failure scenarios under concurrent requests.}
        \resumeItem{Independently designed and developed \textbf{SPHA} (Surgery and Post Hospital Assistance), a full-stack nonprofit healthcare platform supporting seniors post-surgery, built with \textbf{ReactJS}, \textbf{NodeJS/Express}, and \textbf{MongoDB}.}
      \resumeItemListEnd

    \resumeSubheading
      {Sportzzbook}{Oct. 2024 -- Jan. 2025}
      {Software Engineer Intern}{Delhi}
      \resumeItemListStart
        \resumeItem{Built scalable web platforms with \textbf{ReactJS}, optimizing interface performance and responsiveness.}
        \resumeItem{Collaborated on mobile app using \textbf{React Native}, focusing on intuitive design, and resulting in a 15\% increase in user engagement.}
        \resumeItem{Conducted routine performance testing and debugging, reducing platform latency by 20\%.}
      \resumeItemListEnd

    \resumeSubheading
      {AviSoft}{Feb. 2024 -- Aug. 2024}
      {Full Stack Developer Intern}{Jammu, Jammu and Kashmir}
      \resumeItemListStart
        \resumeItem{Migrated client legacy platform from \textbf{AngularJS} to \textbf{NextJS}, achieving 30\% SEO improvement and 40\% faster load times.}
        \resumeItem{Integrated server-side rendering in \textbf{NextJS}, optimizing page speed and reducing server costs by 10\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}


%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{LogicLab} $|$ \emph{NextJS, Next-Auth, TypeScript, Redis, MongoDB, Judge0, AWS, Nginx}}{ \href{https://logiclab.amanmeenia.com}{Link} $|$ \href{https://github.com/Aman-Meenia/logiclab}{Code} }
          \resumeItemListStart
             \resumeItem{Architected and deployed a distributed full-stack coding platform supporting Data Structures \& Algorithms (DSA) practice with real-time code execution. Serves 10+ concurrent active users with 20+ programming problems across multiple difficulty levels.}
            \resumeItem{Implemented secure JWT-based authentication using \textbf{Next-Auth}, integrated Judge0 API for code compilation, and containerized the application using \textbf{Docker} for horizontal scaling and simplified deployment across environments.}
            \resumeItem{Deployed production infrastructure on \textbf{AWS EC2} with \textbf{Nginx} as reverse proxy and load balancer. Achieved 99.9\% uptime, sub-200ms API response times through \textbf{Redis} caching, and optimized MongoDB database queries for high-scale operations.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{ChatSphere} $|$ \emph{NextJS, WebSockets, Next-Auth, Prisma, PostgreSQL, Redis, Shadcn}}{ \href{https://aman-meenia.work.gd/login}{Link} $|$ \href{https://github.com/Aman-Meenia/chatsphere}{Code} }
          \resumeItemListStart
            \resumeItem{Developed a real-time chat application that allows users to send and receive messages instantly, leveraging \textbf{WebSocket} technology for a responsive user experience.}
            \resumeItem{Integrated \textbf{NextAuth} for secure user authentication and \textbf{Prisma} for seamless database interactions with \textbf{PostgreSQL}.}
            \resumeItem{Utilized \textbf{ Redis Pub/Sub} for efficient message handling and scalability, ensuring the application can support a growing user base without performance degradation.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, C/C++, Java, Python} \\
     \textbf{Web and Mobile Technologies}{: ReactJS, React Native, NextJS, ExpressJS, NodeJS, Redux, MongoDB, Prisma, Postgres} \\
     \textbf{Tools and Concepts}{: Data Structures and Algorithms, System Design (HLD and LLD), Distributed Systems Fundamentals, REST APIs, Database Design, WebSockets, Redis, AWS, Nginx, SQL, NoSQL, Docker}\\
     }}

 \end{itemize}
 \vspace{-16pt}



%-----------ACHIEVEMENTS-----------
\section{Achievements}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Google KickStart (Round F)}}{}
          \resumeItemListStart
            \resumeItem{Secured global rank \textbf{696} in Google KickStart.}
          \resumeItemListEnd
          \vspace{-18pt}       \resumeProjectHeading
          {\textbf{LeetCode} 
    \href{https://leetcode.com/u/AmanMeenia0001/}{\textit{amanmeenia0001}}}{}
          \resumeItemListStart
            \resumeItem{Contest Rating: \textbf{2063} (Top 2.37\%)}
            \resumeItem{Solved more than \textbf{1600} problems}
          \resumeItemListEnd
          \vspace{-13pt} % Consistent spacing
    \resumeSubHeadingListEnd
\vspace{-13pt} % Final adjustment to reduce spacing below section
\end{document}\textbf{}
